The function--sheaf dictionary for smooth commutative group schemes over finite fields, with applications over local fields

### 2014-08-20 dictionary.tex
Switch order of 1.3 and 1.4

We close the introduction with a brief description of the structure of this paper.
After setting some basic notation in Section~\ref{sec:notation},
in Section~\ref{sec:category} we define quasicharacter sheaves and give an interpretation of
them as Weil sheaves equipped with an isomorphism of the form \eqref{introbox}.
Section~\ref{sec:Frob} introduces Trace of Frobenius,
one direction of the function--sheaf dictionary.
We define pullbacks and products of quasicharacter sheaves in Section~\ref{sec:pullback}, and use
them to prove a functoriality result on Trace of Frobenius.
In Section~\ref{sec:basechange} we study how quasicharacter sheaves behave under base change
and Weil restriction.
Sections~\ref{sec:bounded} and \ref{sec:finite} describe bounded quasicharacter sheaves and finite quasicharacter sheaves, respectively,
forming two important subcategories of $\QC(G)$.
%These subcategories play a key role in the proof of Proposition~\ref{prop:restriction}.
In Section \ref{sec:connected} we show that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves when $G$ is connected, and that Trace of Frobenius is an isomorphism in this case.
We shift to \'etale group schemes $G$ in Section~\ref{sec:etale} and find a cohomological interpretation
of quasicharacter sheaves in this case.
In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
induces an essentially surjective functor of quasicharacter sheaves.
%Section~\ref{sec:snake} presents the main theorem of this paper: Trace of Frobenius
%is a functorial isomorphism from isomorphism classes of flabby quasicharacter sheaves on $G$
%to characters of $G(\Fq)$.

@@

@@

\begin{proof}
The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
while the second part shows that Trace of Frobenius is a natural transformation
$T: F_1 \to F_2$. When further combined with Proposition~\ref{prop:product},
we see that $F_1$ is an additive functor and $T: F_1 \to F_2$ is a natural
transformation between additive functors,
concluding the proof of Proposition~\ref{prop:functorialG}.
\end{proof}

>>>>

We close the introduction with an overview of the structure of this paper.
After setting some basic notation in Section~\ref{sec:notation},
in Section~\ref{sec:category} we define the category of quasicharacter sheaves.
We define pullbacks and products of quasicharacter sheaves in Section~\ref{sec:pullback}
Section~\ref{sec:Frob} introduces Trace of Frobenius,
one direction of the function--sheaf dictionary.
, and use
them to prove a functoriality result on Trace of Frobenius.
In Section~\ref{sec:basechange} we study how quasicharacter sheaves behave under base change
and Weil restriction.
Sections~\ref{sec:bounded} and \ref{sec:finite} describe bounded quasicharacter sheaves and finite quasicharacter sheaves, respectively,
forming two important subcategories of $\QC(G)$.
%These subcategories play a key role in the proof of Proposition~\ref{prop:restriction}.
In Section \ref{sec:connected} we show that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves when $G$ is connected, and that Trace of Frobenius is an isomorphism in this case.
We shift to \'etale group schemes $G$ in Section~\ref{sec:etale} and find a cohomological interpretation
of quasicharacter sheaves in this case.
In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
induces an essentially surjective functor of quasicharacter sheaves.
%Section~\ref{sec:snake} presents the main theorem of this paper: Trace of Frobenius
%is a functorial isomorphism from isomorphism classes of flabby quasicharacter sheaves on $G$
%to characters of $G(\Fq)$.

@@

We will prove this proposition at the end of Section \ref{sec:pullback}

@@

Using these results on pullbacks we may now prove that Trace of Frobenius is a natural transformation.

\begin{proof}[Proof of Proposition~\ref{prop:functorialG}]
The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
while the second part shows that Trace of Frobenius is a natural transformation
$T: F_1 \to F_2$. When further combined with Proposition~\ref{prop:product},
we see that $F_1$ is an additive functor and $T: F_1 \to F_2$ is a natural
transformation between additive functors,
concluding the proof of Proposition~\ref{prop:functorialG}.
\end{proof}
